---
title: "Replication 2"
author: "Enxhi Buxheli"
date: "2/17/2019"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# attaching libraries
library(dplyr)
library(janitor)
library(tidyverse)
library(xtable)
library(RItools)
library(ri)
library(RColorBrewer)
library(gt)
library(ggplot2)

# eliminates junk output from xtable
options(xtable.comment = FALSE)

# Loading in the data using read_csv instead of read.csv
pnas_data   <- read.csv("dataverse_files/pnas_data.csv")
t1_data     <- read.csv("dataverse_files/t1_data.csv")
prime_data  <- read.csv("dataverse_files/prime_data.csv")
```

```{r hidden_mainresults, include = FALSE}
##main_results.r [ORIGINALLY]
###inference
repeats = c("numberim","Remain","Englishlan")
x.names = paste(repeats,".x",sep="")
y.names = paste(repeats,".y",sep="")
covariates = c('line.x')

###treated first
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('all','no.car')

for(subset in subsets){
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	if(subset == 'all'){
		dat.subset = pnas_data}
	if(subset ==  'no.car'){
		dat.subset = pnas_data[pnas_data$habits != 1,]}
	
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
		
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
		
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		y.mean = mean(dat.use$y.new,na.rm = T)
		y.treat = mean(dat.use$y.new[dat.use$treatment==1],na.rm = T)
	
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = 0)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = disp$greater.p.value
		out.mat[j,6] = disp$lesser.p.value
		out.mat[j,7] = x.sd
		out.mat[j,8] = x.mean
		}
	final.mat = rbind(final.mat,out.mat)
	}

final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','greater.p.value','lesser.p.value','x.sd','x.mean')

final.mat.main = final.mat ##final.mat for output creation later
```

```{r hidden_subset, include = FALSE}
##subset_inference.r [ORIGINALLY]
	
# used to create variables later in the code
repeats = c("numberim","Remain","Englishlan")
x.names = paste(repeats,".x",sep="")
y.names = paste(repeats,".y",sep="")
covariates = c('line.x')
var.names = c('Number of immigrants be increased?','Children of undocumented be allowed to stay?','English as official language?')
	
##dose response estimates comparison
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('ta','tb')

for(subset in subsets){
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	if(subset == 'ta'){
		dat.subset = pnas_data[pnas_data$t.time %in% c('t2a','t4a'),]}
	if(subset == 'tb'){
		dat.subset = pnas_data[pnas_data$t.time %in% c('t2b','t4b'),]}
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
				
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
	
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = ate)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = x.mean
		out.mat[j,6] = x.sd
		out.mat[j,7] = disp$quantile[1]
		out.mat[j,8] = disp$quantile[2]
		}
		final.mat = rbind(final.mat,out.mat)
	}
final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','x.mean','x.sd','quantile.lower','quantile.upper')
final.mat.dose = final.mat ##mat for creating graph later
	
##ideology comparison
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('liberals.only','moderates.only','conservatives.only')

for(subset in subsets){ 
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	if(subset == 'liberals.only'){
		dat.subset = pnas_data[pnas_data$ideology.x %in% c(1,2),]}
	if(subset == 'conservatives.only'){
		dat.subset = pnas_data[pnas_data$ideology.x %in% c(4,5),]}
	if(subset == 'moderates.only'){
		dat.subset = pnas_data[pnas_data$ideology.x == 3,]}
	z.variable = 'treatment'

	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
			
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)

		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = ate)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = x.mean
		out.mat[j,6] = x.sd
		out.mat[j,7] = disp$quantile[1]
		out.mat[j,8] = disp$quantile[2]
		}
	final.mat = rbind(final.mat,out.mat)
	}
final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','x.mean','x.sd','quantile.lower','quantile.upper')
final.mat.ideology = final.mat ##for graph later

##friends comparison
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('low.friends','high.friends','middle.friends')

## Unnecessary line of code

for(subset in subsets){ 
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	if(subset == 'low.friends'){
		dat.subset = pnas_data[pnas_data$Friends.x == 0,]}
	if(subset == 'high.friends'){
		dat.subset = pnas_data[pnas_data$Friends.x >= 5,]}
	if(subset == 'middle.friends'){
		dat.subset = pnas_data[pnas_data$Friends.x > 0 & pnas_data$Friends.x < 5,]}
	
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
			
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = ate)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = x.mean
		out.mat[j,6] = x.sd
		out.mat[j,7] = disp$quantile[1]
		out.mat[j,8] = disp$quantile[2]
		}
	final.mat = rbind(final.mat,out.mat)
	}
	final.mat = as.data.frame(final.mat)
	colnames(final.mat) = c('variable','subset','N','ate','x.mean','x.sd','quantile.lower','quantile.upper')
	final.mat.friends = final.mat ##for graph
	
#######income subsets
subsets = c('low.income','middle.income', 'high.income')
final.mat = matrix(nrow = 0, ncol = 8)

for(subset in subsets){ 
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	
	if(subset == 'low.income'){
		dat.subset = pnas_data[pnas_data$income.new < 105000,]
		}
	if(subset == 'middle.income'){
		dat.subset = pnas_data[pnas_data$income.new >= 105000 & pnas_data$income.new <= 135000,]
		}
	if(subset == 'high.income'){
		dat.subset = pnas_data[pnas_data$income.new > 135000,]
		}
	
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
			
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
				
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)

		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = ate)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = x.mean
		out.mat[j,6] = x.sd
		out.mat[j,7] = disp$quantile[1]
		out.mat[j,8] = disp$quantile[2]
		}
	final.mat = rbind(final.mat,out.mat)
	}
final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','x.mean','x.sd','quantile.lower','quantile.upper')
final.mat.income = final.mat  ##for later
```

```{r hidden_prime, include = FALSE}
##primetest.r [ORIGINALLY]
###use randomization inference to look for changes in responses induced by experiment in subsets by covariates.

#####recodes
####race variable
prime_data$non.white = ifelse(prime_data$race_4 == 1, 1,0)
prime_data$non.white[is.na(prime_data$non.white)==T] = 0
prime_data$residency.new[prime_data$residency == 1] = 1
prime_data$residency.new[prime_data$residency == 2] = 3.5
prime_data$residency.new[prime_data$residency == 3] = 7.5
prime_data$residency.new[prime_data$residency == 4] = 12.5
prime_data$residency.new[prime_data$residency == 5] = mean(prime_data$age, na.rm = T)-15
prime_data$residency.new[prime_data$residency == 6] = mean(prime_data$age, na.rm = T)

#####recodes
###English language is reverse coded from other variables:
prime_data$Englishlan.x = recode(prime_data$Englishlan.x, 
                                 "5" = "1", "4" = "2", "2" = "4", "1" = "5")
prime_data$Englishlan.y = recode(prime_data$Englishlan.y, 
                                 "5" = "1", "4" = "2", "2" = "4", "1" = "5")

###gender recode
prime_data$male = ifelse(prime_data$gender == 1, 1, 0)

###inference
repeats = c("numberim","Remain","Englishlan")

x.names = paste(repeats,".x",sep="")
y.names = paste(repeats,".y",sep="")

covariates = c('line')
final.mat = matrix(nrow = 0, ncol = 8)
subsets = c('all.prime')

for(subset in subsets){ ##b.only, complier, and non-compler subsets
	out.mat = matrix(nrow = length(repeats), ncol = 8)
	dat.subset = prime_data
		
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
			
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
			
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable])
		probs = genprobexact(Z = dat.use[,z.variable])
		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
	
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = 0)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
		
		##fill matrix
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = disp$greater.p.value
		out.mat[j,6] = disp$lesser.p.value
		out.mat[j,7] = x.sd
		out.mat[j,8] = x.mean
		}
		final.mat = rbind(final.mat,out.mat)
		}
	final.mat = as.data.frame(final.mat)
	colnames(final.mat) = c('variable','subset','N','ate','greater.p.value','lesser.p.value','x.sd','x.mean')
	
	final.mat.prime = final.mat ##mat for creating output later
```

# Table 1
```{r, results='asis'}
#output_create.r [ORIGINALLY]
####create output
output.vars = c('numberim','Remain','Englishlan')
var.names = c('Number of immigrants be increased?',
              'Children of undocumented be allowed to stay?',
              'English as official language?')

##main results
##cumalative results output
final.mat.use = rbind(final.mat.main,final.mat.prime)
final.mat.use$greater.p.value = as.numeric(as.character(final.mat.use$greater.p.value)); final.mat.use$lesser.p.value = as.numeric(as.character(final.mat.use$lesser.p.value)); final.mat.use$ate = as.numeric(as.character(final.mat.use$ate)); final.mat.use$x.mean = as.numeric(as.character(final.mat.use$x.mean)); final.mat.use$x.sd = as.numeric(as.character(final.mat.use$x.sd)); final.mat.use$N = as.numeric(as.character(final.mat.use$N))
final.mat.use$p.value = final.mat.use$greater.p.value
final.mat.redact = final.mat.use[,c('variable','subset','ate','p.value','x.mean','x.sd','N')]
final.mat.redact[,c('ate','p.value','x.mean','x.sd')] = round(final.mat.redact[,c('ate','p.value','x.mean','x.sd')],3)
final.mat.redact$ate.new = paste(final.mat.redact$ate,' (',final.mat.redact$p.value,')',sep='')
final.mat.redact$x.mean.new = paste(final.mat.redact$x.mean,' (',final.mat.redact$x.sd,')',sep='')
out.mat.a = final.mat.redact[final.mat.redact$subset == 'all'&final.mat.redact$variable %in% output.vars,]
out.mat.a = final.mat.redact[final.mat.redact$subset == 'all'&final.mat.redact$variable %in% output.vars,c('ate.new')]	
out.mat.c = final.mat.redact[final.mat.redact$subset == 'no.car'&final.mat.redact$variable %in% output.vars,c('ate.new')]
out.mat.x = final.mat.redact[final.mat.redact$subset == 'all'&final.mat.redact$variable %in% output.vars,c('x.mean.new')]
Ns = c('N',max(final.mat.redact$N[final.mat.redact$subset=='all']),
max(final.mat.redact$N[final.mat.redact$subset=='no.car']),
max(final.mat.redact$N[final.mat.redact$subset=='all']))

h1 = c('',paste('(',1:3,')',sep = ''))
h2 = c('','all respondents','waits on platform','all respondents ')
h3 = c('question','ATE (P)*','CATE (P)','T1 levels (SD)')
hs = rbind(h1,h2,h3)
row.names(hs) = NULL
	
out.mat = cbind(out.mat.a,cbind(out.mat.c,out.mat.x))
out.mat = cbind(var.names,out.mat)
out.mat = rbind(out.mat,Ns)
out.mat = rbind(hs,out.mat)

# Replication for table 1
# cols <- c(2:nrow(out.mat))

table_1 <- as_tibble(out.mat[,2:ncol(out.mat)])
table_1 <- row_to_names(table_1, 2)
out.table <- xtable(table_1, digits = 3,
                    align = "lccc")

# Adding user friendly names/labels in the final table 1
colnames(out.table) <- c('All respondents', 'Waits on platform', 'All respondents ')
rownames(out.table) <- c("Question", "Number of immigrants be increased?†",
                       "Children of undocumented be allowed to stay?", "English as official language?", "n")

# outputting gt table with comments
gt(out.table, rownames_to_stub = TRUE) %>% 
  tab_source_note(source_note = 'In the first "All respondents" column, ATE represents responses in T2-T1 
                  for the treatment group compared with the control group for the entire experimental sample.
                  Positive values mean a more politically conservative response. In the "Waits on platform"
                  column, CATEs are the Conditional Average Treatment Effects for persons who said they stand
                  on the platform, rather than wait in their cars. In the second "All Respondents" column, T1
                  levels and SDs for each variable for all respondents. All variables scaled 0-1.') %>% 
  tab_source_note(source_note = '* P values from a one-tailed test against the Null Hypothesis of no effect
                  are in parentheses.') %>% 
  tab_source_note(source_note = '† Each of the questions allowed responses on a five-point scale ranging from
                  strongly agree to strongly disagree (exact answers were changed to be appropriate to the
                  actual question)')
  
```

# Figure 2
```{r}
# ####create output
output.vars = c('numberim','Remain','Englishlan')
var.names = c('Number of immigrants be increased?','Children of undocumented be allowed to stay?','English as official language?')

##graph presets
os = .4
line.os = .015
y.point = .75
ylims = c(0,1.1)
xlims = c(-.35,.35)
points.cex = 4
lab.cex = 1.5
line.lwd = 4.5
axis.cex = 1.25

colors = brewer.pal(3,'Paired')[1:2] ##colors for pairs used in plots below

par(mfrow = c(3,1)) 
par(mar = c(5,0,1,0))
par(bty = 'n')

##dose response graph
out.mat = final.mat.dose[,c('variable','subset','ate','quantile.lower','quantile.upper')]
out.mat$ate = as.numeric(as.character(out.mat$ate))
out.mat$quantile.lower = as.numeric(as.character(out.mat$quantile.lower))
out.mat$quantile.upper = as.numeric(as.character(out.mat$quantile.upper))

out.mat.ta = out.mat[out.mat$subset == 'ta'&out.mat$variable %in% output.vars,]
out.mat.tb = out.mat[out.mat$subset == 'tb'&out.mat$variable %in% output.vars,]

for(i in 1:length(var.names)){
	plot(x  = out.mat.ta$ate[i], y = y.point, 
		xlim = xlims,
		ylim = ylims,
		ylab = '',
		xlab = var.names[i],
		yaxt = 'n',
		type = 'n',
		cex.lab = lab.cex,
		cex.axis = axis.cex)
	lines(x = c(out.mat.ta$quantile.lower[i],out.mat.ta$ate[i]-line.os), 
			y = c(y.point,y.point),
			lty = 1,
			col = colors[1],
			lwd = line.lwd)
	lines(x = c(out.mat.ta$ate[i]+line.os,out.mat.ta$quantile.upper[i]), 
			y = c(y.point,y.point),
			lty = 1,
			col = colors[1],
			lwd = line.lwd)
	lines(x = c(out.mat.tb$quantile.lower[i],out.mat.tb$ate[i]-line.os), 
			y = c(y.point-os,y.point-os),
			lty = 1,
			col = colors[2],
			lwd = line.lwd)
	lines(x = c(out.mat.tb$ate[i]+line.os,out.mat.tb$quantile.upper[i]), 
			y = c(y.point-os,y.point-os),
			lty = 1,
			col = colors[2],
			lwd = line.lwd)

	points(x  = out.mat.ta$ate[i], y = y.point,
		pch = 19,
		cex = points.cex,
		col = colors[1])
	points(x  = out.mat.tb$ate[i], y = y.point - os,
		pch = 1,
		cex = points.cex,
		col = colors[2])
}
```

\newpage

# Table 2
```{r, results='asis'}
## Here I used the balance_check.r code and compared the balance_table.tex output to the 
## original article to ensure that the results were replicated. Here, I am just putting it
## all together in a code chunk. I maintained the majority of their variable names and here
## just changed the code so that it would use read_csv instead of read.csv. I also eliminated
## some of the other analyses that Enos had run which was not necessary for performing the 
## replication. The xBalance function is used to calculate the standardized mean differences 
## from each covariate.
balance_table <- xBalance(treatment ~ liberal+republican+obama.disapprove+ride.everyday+voted.2010+romney.voter+Hispanics.x+age+residency.new+college+male+hispanic.new+white+income.new, 
                            data = pnas_data, 
                            report = c("std.diffs","z.scores","adj.means","chisquare.test")[1:3], 
                            strata = factor(pnas_data$station))

## Outputs the results for Table 2 in the replication document. 
balance_xtable <- xtable(balance_table$results[,1:4,], 
                         label="Table 2. Covariate balance across treatment conditions", 
                         digits= 2,
                         align = "lrrrr")

# Adding user friendly names/labels in the final table 2
rownames(balance_xtable) <- c("Liberal†", "Republican", "Obama disapprove", "Ride MBTA every day", "Voted 2010", "Romney voter", "Hispanic threat", "Age", "Residency year", "College", "Male", "Hispanic", "White", "Income")
colnames(balance_xtable) <- c("Control", "Treatment", "Standard Difference*", "Z Score")

gt(balance_xtable, rownames_to_stub = TRUE) %>% 
  tab_source_note(source_note = '* Difference in standardized units.') %>% 
  tab_source_note(source_note = '† Mean response values for pretreatment variables accounting for
                  stratification into train stations. All variables are 0 and 1 variables, except 
                  for Hispanic threat, which is a seven-point scale indicating how threatening respondents
                  find Hispanics, recoded 0–1; residency, which is measured in years; and income, which is
                  annual income in dollars.') %>% 
  fmt_number(columns = everything(), decimals = 2)
```

\newpage
# Extensions
## Table 2 - Presented Visually
```{r}
x <- as.data.frame(RItools:::prepareXbalForPlot(balance_table))
rownames(x) <- c("Liberal", "Republican", "Obama disapprove", "Ride MBTA every day", "Voted 2010", "Romney voter", "Hispanic threat", "Age", "Residency year", "College", "Male", "Hispanic", "White", "Income")
x <- rownames_to_column(x)

ggplot(x, aes(x = strat, y = rowname)) +
  geom_point() + 
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(title = "Standard Difference across Treatment Conditions",
       x = "Standard Difference",
       y = "Treatment Condition") +
  theme_classic()
  
```

\newpage
\newpage
# References
(1) Enos, Ryan D. 2014. “Causal Effect of Intergroup Contact on Exclusionary Attitudes.” Proceedings of the National
    Academy of Sciences 111 (10). National Acad Sciences.

(2) Enos, Ryan, 2017. "Replication Data for: The Causal Effect of Intergroup Contact on Exclusionary  \newline
    Attitudes", https://doi.org/10.7910/DVN/DOP4UB, Harvard Dataverse, V1, \newline 
    UNF:6:xkxAAeLJ6AIYRu1C+C1FSQ== [fileUNF]





